---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# touringplans

<!-- badges: start -->
<!-- badges: end -->

The goal of touringplans is to provide access to Disney World Ride Wait Time Datasets curated by the TouringPlans.com team.

## Installation

<!-- You can install the released version of touringplans from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("touringplans") -->
<!-- ``` -->

You can install the development version of touringplans with:
```{r, eval = FALSE}
devtools::install_github("LucyMcGowan/touringplans")
```


You can find a list of all data sets along with variable information on [the touringplans package website](https://lucymcgowan.github.io/touringplans)

## Example

The `touringplans_2018` data frame contains wait time data aggregated by hour for 14 attractions, along with some park-level daily metadata. The example below demonstrates how wait times by day are associated with the Ticket Season. The example below uses the tidyverse package to assist with data wrangling.

```{r, message = FALSE, warning = FALSE}
library(touringplans)
library(tidyverse)
touringplans_2018 %>%
  count(name)
```

We can aggregate the hourly posted wait time data into an avarage wait time by day for each ride. 

```{r}
agg_2018 <- touringplans_2018 %>%
  group_by(date, name, wdw_ticket_season) %>%
  summarise(average_diff = mean(avg_spostmin - avg_sactmin, na.rm = TRUE), .groups = "drop") %>%
  filter(average_diff > -300) # remove weird data points (more on this later!)
```

```{r}
lm(average_diff ~ wdw_ticket_season, data = agg_2018) %>%
  summary()
```

```{r, fig.height = 6}
ggplot(agg_2018, aes(x = date, y = average_diff)) +
  geom_point(aes(color = wdw_ticket_season)) +
  geom_line() +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~ name, ncol = 2) + 
  labs(y = "Average posted wait time",
       color = "Ticket Season")
```

