---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# touringplans

<!-- badges: start -->
<!-- badges: end -->

The goal of touringplans is to provide access to Disney World Ride Wait Time Datasets curated by the TouringPlans.com team.

## Installation

<!-- You can install the released version of touringplans from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("touringplans") -->
<!-- ``` -->

You can install the development version of touringplans with:
```{r}
devtools::install_github("LucyMcGowan/touringplans")
```


## Example

For example, the following code looks at the Toy Story Mania! posted and actual wait times. We look at the difference in average posted and actual wait times within each hour in January - May 2019, then average these across days and plot them.

```{r}
library(touringplans)
library(tidyverse)

toy_story_mania %>%
  filter(date >= as.Date("2019-01-01"), date <= as.Date("2019-05-31")) %>%
  mutate(hour = lubridate::hour(datetime)) %>%
  group_by(date, hour) %>%
  summarise(avg_post = mean(spostmin, na.rm = TRUE),
            avg_act = mean(sactmin, na.rm = TRUE),
            diff = avg_post - avg_act, .groups = "drop") %>%
  group_by(date) %>%
  summarise(m = mean(diff, na.rm = TRUE)) -> toy_story_summary
ggplot(toy_story_summary, aes(x = date, y = m)) + 
  geom_point() +
  labs(y = "Average difference between posted and \nactual wait times (minutes)")
```

The `touringplans_metadata` is a data frame that contains metadata about the parks. This can be merged with the individual ride datasets. For example, the code below demonstrates how to merge the metadata with the `toy_story_summary` data curated above and recreate the plot, colored by ticket season.

```{r}

toy_story_summary %>%
  left_join(touringplans_metadata, by = "date") %>%
  ggplot(aes(x = date, y = m, color = wdw_ticket_season)) + 
  geom_point() +
  labs(y = "Average difference between posted and \nactual wait times (minutes)", 
       color = "Ticket Season") 
```
